`mathml`: Translate R Expressions to MathML and LaTeX

### 2023-11-22 rj/mathml.Rmd
final proof IA

This case study describes a model by Schwarz [-@schwarz1994] from mathematical
psychology using the features of package \pkg{mathml}. Schwarz [-@schwarz1994]
presents a new explanation of redundancy gains that occur when observers respond
to stimuli of different sources, and the same information is presented on two or
more channels. In Schwarz' [-@schwarz1994] model, decision-making builds on a
process of noisy accumulation of information over time [e.g., @ratcliff2016]. In
redundant stimuli, the model assumes a superposition of channel-specific
diffusion processes that eventually reach an absorbing barrier to elicit the
response. For a detailed description the reader may refer to the original
article.

@@

Schwarz [-@schwarz1994] applied the model to data from a redundant signals 
task [@miller] with 13 onset
asynchronies \(0, \pm33, \pm67, \pm100, \pm133, \pm167, \pm\infty\) ms,
where \(\tau = 0\) refers to the synchronous condition, and \(\pm\infty\) to the
single-target presentations. Each condition was replicated 400 times. The
observed mean response times and their standard deviations are given in
Table \@ref(tab:miller-data) below.

>>>>

This case study describes a model by Schwarz [-@schwarz1994] from mathematical
psychology using the features of package \pkg{mathml}. Schwarz [-@schwarz1994]
presents a new explanation of redundancy gains that occur when observers respond
to stimuli of different sources, and the same information is presented on two or
more channels. In Schwarz's [-@schwarz1994] model, decision-making builds on a
process of noisy accumulation of information over time [e.g., @ratcliff2016]. In
redundant stimuli, the model assumes a superposition of channel-specific
diffusion processes that eventually reach an absorbing barrier to elicit the
response. For a detailed description the reader may refer to the original
article.

@@

Schwarz [-@schwarz1994] applied the model to data from a redundant signals 
task [@miller] with 13 onset
asynchronies \(0, \pm33, \pm67, \pm100, \pm133, \pm167, \pm\infty\) ms,
where \(\tau = 0\) refers to the synchronous condition, and \(\pm\infty\) to the
single-target presentations. Each condition was replicated 400 times. The
observed mean response times and their standard deviations are given in
Table \@ref(tab:miller-data).
